Index measures for oak decline severity using phenotypic descriptors

### 2019-12-12 manuscript/manuscript.Rmd
added equations for newly added additional descriptors

- Site types
- Descriptor types
- Field phenotyping protocol
- Crown assessments
- Stem assessments - 2m base, 3m base

@@

A total of 30 phenotypic descriptors were collected relating to the trees shape, size, crown condition and the presence of biotic agents including insects, bacteria and fungi.
These descriptors are shown in Table #.
Crown radius, canopy closure and tap tests for dead stem tissue were measured for each cardinal point.
AOD stem symptoms (active bleeds, black staining, callused wounds) were collected from the basel 3m of the stem.
Each individual 
All trees were manually assigned a decline status category; control, AOD, COD or remission.

@@

@@

@@

>>>>

- Site types
- Field phenotyping protocol
- Crown assessments
- Stem assessments - 2m base, 3m base

@@

A total of 30 phenotypic descriptors were collected relating to the trees shape, size, crown condition and the presence of biotic agents including insects, bacteria and fungi.
These descriptors are shown in Table #.
Crown radius, canopy closure and tap tests for dead stem tissue were measured for each cardinal point.
The crown radius was
The AOD stem symptoms (active bleeds, black staining, callused wounds) were collected by measuring longest axis of each individual bleed, stain or callused wound found within the basal 3m of the stem (ref).
The frequency of *A. biguttatus* exit holes were counted along with the presence or absence of each of oval shaped exit holes, small circular shaped exit holes and ground level fungal fruiting bodies were recorded from the basal 2m of the stem (ref). 
All trees were manually assigned a decline status category; control, AOD, COD or remission.

@@

$$R = \frac{(h-l)}{h} \times 100$$

$h$ = total height (m), $l$ = lower crown height (m)

@@

$$S = \frac{4\pi(h-l)}{3r^2} \left[ \left( r^2 + \frac{r^4}{4(h-l)^2} \right) ^{1.5} - \left( \frac{r^4}{4(h-l)^2} \right) ^{1.5} \right] \times c $$

$r$ = crown radius (m), $h$ = total height (m), $l$ = lower crown height (m), c = crown condition (%)

@@

$$e = \frac{S}{v}$$

$S$ = composite crown surface area (m^2^), $v$ = composite crown volume (m^3^)
